Pulling oral and IV data from CvTdb

### 2023-05-10 invivopkfit/data-raw/pulling_oral_iv_data_cvtdb.Rmd
Workflow now functions at all steps: setup, preprocessing, prefit, fitting, summary. Methods for coef(), residuals(), predict(), logLik(), AIC(), and BIC() added, along with new method for rmse(). Built in models for flat, 1comp, and 2comp are included. (get_starts_2comp.R still needs work)

---
title: "Pulling oral and IV data from CvTdb"
author: "Caroline Ring"
date: "2022-12-13"
output: html_document
---

@@

I don't fully know what all of this means, but it filters out various "internal" tables that are not actually part of CvTdb, and shows only the tables that are.

@@

Save the pulled CVT data with the edits/normalizations

```{r}
this_date <- "2023_01_05"
write.csv(cvt_data,
          paste0("../inst/ext/cvt_data_",
          this_date,
          ".csv"),
          row.names = FALSE)
```

>>>>

---
title: "Pulling oral and IV data from CvTdb"
author: "Caroline Ring"
date: "2023-05-10"
output: html_document
---

@@

I don't fully know what all of this SQL query means, but it filters out various "internal" tables that are not actually part of CvTdb, and shows only the tables that are.

@@

To save space, filter CVT data to oral/IV routes and blood/plasma media, because nothing else is implemented right now. Also filter down to cases where administered and analyzed DTXSID are the same.

```{r}
cvt <- cvt_data[studies.administration_route_normalized %in% c("oral", "iv") &
                  series.conc_medium_normalized %in% c("blood", "plasma") &
                  chemicals_dosed.dsstox_substance_id == chemicals_analyzed.dsstox_substance_id]
```

```{r}
getwd()
```

Save the pulled CVT data with the edits/normalizations, andf also save the current date.

```{r}
cvt_date <- Sys.Date()
save(cvt, file = "../data/cvt.rda", compress = "bzip2")
save(cvt_date, file = "../data/cvt_download_date.rda")
```
